Automating Verification of MPC Security: $\metaprot$ to $\minifed$

### 2023-07-07 popl24/scratch.tex
checkpoint

Certifications will demonstrate probabilistic independence of input
wire lables and garbled tables in a program's basic distribution, so
we need to consider dependencies of flips and gate views. Thus we make
the following definitions:
  We write $\progtt(\prog)$ to denote the \emph{basic distribution} of
  $\prog$ as defined in Definition \ref{def-progd}. For any program $\prog =
  (\eassign{v_1}{\be_1};\ldots;\eassign{v_n}{\be_n})$, define
  $\vdefs(\prog) \defeq \{ v_1,\ldots,v_n \}$.
We also need to formalize notions of probabilistic independence, aka
\emph{separation}, and correlation. We borrow the symbols $*$ and $\sim$
from \cite{barthe2019probabilistic} with the same denotations.
  We write $\vc{\pdf{X}}{x}{y}$ iff $\pdf{X}(\{ x \mapsto 0\}\ |\ \{ y \mapsto 0 \}) =
  \pdf{X}(\{ x \mapsto 1\}\ |\ \{ y \mapsto 1 \}) = 1$.
  We write $\sep{\pdf{X}}{Y}{Z}$ iff for all
    $\store \in \mems(X \cup Y)$:
  $$(\margd{\pdf{X}}{Y \cup Z})(\store) =
  (\margd{\pdf{X}}{Y})(\store_Y) * (\margd{\pdf{X}}{Z})(\store_Z)$$ 
It is also necessary to define notions of correlation with wire

@@

@@

\begin{definition}[Gate Certification]
  \label{definition-gate-certification}
Let $\mathit{gate}$ be a gate function. For $1 \le i \le 4$  let:
  \config{\varnothing}{\ttt{v[0,out] := } e_i}\redxs\config{\prog_i}{\ttt{()}}
  where

@@

  Then $\mathit{gate}$ is \emph{certified} iff for all $1 \le i \le 4$:
  \sep{\progtt(\prog_i)}{X}{\vdefs(\prog_i)} 
  \quad \text{and} \quad \gc{\progd(\prog_i)}{\vx{0}{out}}{\ttt{owl(c)}}

@@

\begin{definition}[Encode Certification]

@@

  \item $\gc{\progd(\prog,v_1)}{\itv}{\ttt{owl(s1)}} \quad \text{and} \quad
    \gc{\progd(\prog,v_2)}{\itv}{\ttt{owl(s2)}}$
  \item $\sep{\progd(\prog,v_2)}{\{\ttt{s[2,s2]\}}}{(\vdefs(\prog) \cup \itv)}$

@@

\begin{definition}[Decode Certification]

@@

  \redxs \config{\prog_1}{\be_1}
  \quad \text{and} \quad
  \config{\varnothing}{\mathit{decode}(\ttt{c}, \ttt{invert(owl(c))})}
  \redxs \config{\prog_0}{\be_0}

@@

  \sep{\progtt(\prog_i)}{\ttt{\{flip[2,gate:c.k],flip[2,gate:c.p]\}}}{\vdefs(\prog_i)}

@@

  \label{lemma-certification}

@@

\subsubsection{Correctness of Certified Components}
\label{section-composition-metatheory}

To demonstrate correctness of certification, we need to show that
isolated component certificates preserve relevant properties
when integrated into larger programs. This resonates with
\emph{framing} as developed in \cite{barthe2019probabilistic}.
In the following we will use $f$ to range over flips.
First, we show that if a flip $f$ is independent from the views
in a protocol (as is the case with input labels used to
encode a garbled table), then separation from views that
use $f$ (e.g., in an output label) is preserved. 
\begin{lemma}[Wire Framing]
  \label{lemma-wire-framing}
  If $\sep{\progtt(\prog)}{\{f\}}{\vdefs(\prog)}$ for flip $f$ and
  $\vars(\prog) \cap \vars(\prog') = \{ f \}$ then
  $\sep{\progtt(\prog';\prog)}{\vdefs(\prog')}{\vdefs(\prog)}$.
\end{lemma}
Next, we show that output correlations (e.g., between output wire values and
labels) are preserved by substitution of correlated values for flips (e.g.,
between input wire values and labels).
\begin{lemma}[Substitution]
  \label{lemma-substitution}
  If $\vc{\progtt(\prog,\be)}{\itv}{f}$ and $\vc{\progtt(\prog',\be')}{\itv}{f'}$
  and $\sep{\progtt(\prog';\prog)}{\vdefs(\prog')}{\vdefs(\prog)}$
  then $\vc{\progtt(\prog';\prog,\be[\be'/f'])}{\itv}{f}$.
\end{lemma}
Our wire framing and substitution Lemmas then allow us to generalize
certification of gates and encoding to arbitrary circuit contexts,
assuming that outputs are not wired to multiple inputs \cite{tate2003garbled,nieminen2023breaking}.
\begin{lemma}[Gate Composition]
  \label{lemma-compose}
Given well-typed $\prog_1;E[\mathit{gate}(g,g_1,g_2,v_1,v_2)]$ and certified $\mathit{gate}$ where:
$$
\config{\prog_1}{E[\mathit{gate}(g,g_1,g_2,v_1,v_2)]} \redxs \config{\prog_1;\prog_2}{E[v]}
$$
If the following preconditions hold:
\begin{enumerate}
\item $\{ g_1 \} \cap \{ g_2 \} \cap \wired(\prog_1) = \varnothing$ and $g \not\in \prog_1$
\item $\gc{\progd(\prog_1)}{v_1}{\owl(g_1)}$ and $\gc{\progd(\prog_1)}{v_2}{\owl(g_2)}$
\end{enumerate}
then we have as postconditions:
\begin{enumerate}
  \item $\gc{\progd(\prog_1;\prog_2)}{v}{\owl(g_2)}$
  \item $\sep{\progd(\prog_1;\prog_2,v)}{\vdefs(\prog_1)}{\vdefs(\prog_2) \cup \{\itv\}}$
\end{enumerate}
\end{lemma}
\begin{proof}
  Given that $g_1$ and $g_2$ are distinct and not wired in $\prog_1$
  we are assured that $\ttt{owl}(g_1)$ and $\ttt{owl}(g_1)$ are in
  independent uniform distributions, and given that $g \not\in
  \prog_1$ we are assured that $\ttt{owl}(g)$ contains entirely fresh
  flips. Thus, precondition 2, Lemma \ref{lemma-wire-framing}, and
  Definition \ref{definition-gate-certification} imply postcondition
  2.  Furthermore, since gate certification guarantees that
  correlation with $\ttt{owl}(g)$ is guaranteed under all possible gate
  input wire values, precondition 2 and Lemma \ref{lemma-substitution}
  guarantee postcondition 2.
\end{proof}

\begin{lemma}[Decode Composition]
  \label{lemma-decode}
Given well-typed $\prog_1;E[\mathit{decode}(g,v)]$ and certified $\mathit{decode}$ where 
$$
\config{\prog_1}{E[\ttt{decode}(g,v)]} \redxs \config{\prog_1;\prog_2}{E[\be]}
$$
If the following preconditions hold:
\begin{enumerate}
\item $g \not\in \cap \wired(\prog_1)$
\item $\gc{\progd(\prog_1)}{v}{\owl(g)}$
\end{enumerate}
then we have as postcondition:
\begin{enumerate}
  \item $\sep{\progd(\prog_1;\prog_2)}{\vdefs(\prog_1)}{\vdefs(\prog_2)}$
\end{enumerate}
\end{lemma}
Given the above, we can establish that any circuit built with certified
components is passive secure. 
\begin{theorem}
  \label{theorem-ygc-NIMO}
  If $e$ is a well-typed YGC circuit definition using certified components
  where no gate output is wired more than once, and $\config{\varnothing}{e}
  \redxs \config{\prog}{\varnothing}$, then $\NIMO(\prog)$. 
\end{theorem}

\begin{proof}
  Let $\iov(\prog) = S \cup (V \cup \outv)$. Noting that any
  encoding necessarily uses entirely fresh variables by Definition and
  type safety, by applying Lemmas \ref{lemma-compose} and
  \ref{lemma-decode} and the frame rule of
  \cite{barthe2019probabilistic} we obtain:
  $$
  \sep{\progd(\prog)}{(S_{\{2\}}\cup\{\outv\})}{V}
  $$
  Noting that the garbler (client 2) has no views, this means that
  the garbler's secrets are independent of the evaluator's views. The
  result follows by Definition \ref{definition-NIMO}.
\end{proof}

@@

Theorem \ref{theorem-nimo} means that any well-typed program using
$\ttt{encode}$, $\ttt{andgg}$, and $\ttt{decode}$ will generate a
circuit that is passive secure, provided that gate outputs are not
used more than once. To add an $\ttt{or}$ gate to our library, we can
use $\ttt{andgg}$ as a template, in fact simple modification of
$\ttt{andtable}$ is all that would be needed. Thus, this library
embodies a Fairplay-like language where well-typedness of metaprograms
guarantees safety and security of generated protocols.

The requirements that output wire labels are not used more than once
reflects a known result, that naive copy gate output is unsound in
YGC- i.e., passive security fails. In fact, we are unable to
automatically verify $\gNIMO$ for $\ttt{andgg}$ without the assumption
that input wire lables are in independent uniform distributions. We
can capture the necessary fix as in Figure \ref{fig-ygc-copy}. The
garbler creates a copy gate with two new output wire labels in
independent uniform distributions (in \ttt{copygate}), and permutes
them using the input wire label pointer after encrypting with the
input wire label keys. The evaluator then recovers the encrypted
output wire values during evaluation (in \ttt{evalcopy}). Given an
$\ttt{orgg}$ gate defined as outlined abotve, we can then use
secure $\ttt{copy}$ as follows: 
\begin{verbatimtab}
  let s = encode(s1,s2) in
  let s1c = copy(c1s1,c2s1,s1,s.wv1) in
  let s2c = copy(c1s2,c2s2,s2,s.wv2) in
  let wv1 = andgg(1,c1s1,c1s2,s1c.wv1,s2c.wv1) in
  let wv2 = orgg(2,c2s1,c2s2,s1c.wv2,s2c.wv2) in
  decode(3,andgg(3,1,2,wv1,wv2))
\end{verbatimtab}
These definitions of $\ttt{copy}$ and $\ttt{orgg}$ have been
automatically verified as in Section \ref{section-pre-post} for
$\ttt{andgg}$. In general, any new gate form- such as optimized gates
\cite{XXX}- can be verified automatically in a similar way.

>>>>

It is necessary to define notions of correlation with wire

@@

  \label{definition-gc}

@@

\begin{definition}[YGC Gate Certification]
  \label{definition-ygcgate-certification}
  Let $\mathit{gate}$ be a gate function.
  For $1 \le i \le 4$  let
  $
  \config{\varnothing}{e_i}\redxs\config{\prog}{v_i}
  $
  where:

@@

  Then $\mathit{gate}$ is \emph{certified} iff the following conditions hold:
  \item $\sep{\progtt(\prog)}{X}{\vdefs(\prog)}$
  \item For all $1 \le i \le 4$, $\gc{\prog}{v_i}{\ttt{c}}$

@@

\begin{definition}[YGC Encode Certification]
  \label{definition-ygcencode-certification}

@@

  \item $\gc{\prog}{v_1}{\ttt{s1}} \quad \text{and} \quad \gc{\prog}{v_2}{\ttt{s2}}$
  \item $\sep{\progd(\prog)}{\{\ttt{s[1,s1]\}}}{\vdefs(\prog)_{\{2\}}}$
  \item $\sep{\progd(\prog)}{\{\ttt{s[2,s2]\}}}{\vdefs(\prog)_{\{1\}}}$    
  \item All $x \in \vars(\prog)$ are distinguished by $\ttt{in1}$ or $\ttt{in2}$. 

@@

\begin{definition}[YGC Decode Certification]
  \label{definition-ygdecode-certification}

@@

  \redxs \config{\prog}{\be}
  %\quad \text{and} \quad
  %\config{\varnothing}{\mathit{decode}(\ttt{c}, \ttt{invert(owl(c))})}
  %\redxs \config{\prog}{\be_0}

@@

  \sep{\progtt(\prog)}{\ttt{\{flip[2,gate:c.k],flip[2,gate:c.p]\}}}{\vdefs(\prog)}

@@

  \label{lemma-ygc-certification}

@@

\subsubsection{Gate Invariants and Circuit Security}
\label{section-composition-metatheory}

To demonstrate correctness of certification, we need to show that
isolated component certificates preserve relevant properties
when integrated into larger programs. 
%First, we show that if a flip $f$ is independent from the views
%in a protocol (as is the case with input labels used to
%encode a garbled table), then separation from views that
%use $f$ (e.g., in an output label) is preserved. 
%\begin{lemma}[Wire Framing]
%  \label{lemma-wire-framing}
%  If $\sep{\progtt(\prog)}{\{f\}}{\vdefs(\prog)}$ for flip $f$ and
%  $\vars(\prog) \cap \vars(\prog') = \{ f \}$ then
%  $\sep{\progtt(\prog';\prog)}{\vdefs(\prog')}{\vdefs(\prog)}$.
%\end{lemma}
%Next,
First we establish another substitution result, showing that
correlations (e.g., between output wire values and labels) are
preserved by substitution of correlated values for flips (e.g.,
between input wire values and labels).
\begin{lemma}[Substitution$\sim$]
  \label{lemma-substitution-sim}
  If $\vc{\progtt(\prog_2,\be)}{\itv}{f}$ and $\vc{\progtt(\prog_1,\be')}{\itv}{f'}$
  and $\vars(\be') \cap (\vars(\be) - \{ f \}) = \varnothing$
  then $\vc{\progtt(\prog_1;\prog_2,\be[\be'/f'])}{\itv}{f}$.
\end{lemma}
Now we can show how to splice gates into arbitrary circuits in an
invariant-preserving manner, assuming that outputs are not wired to
multiple inputs \cite{tate2003garbled,nieminen2023breaking}.
\begin{lemma}[YGC Gate Invariant]
  \label{lemma-ygc-preservation}
Given well-typed $\prog_1;E[\mathit{gate}(g,g_1,g_2,v_1,v_2)]$ and certified $\mathit{gate}$ where:
$$
\config{\prog_1}{E[\mathit{gate}(g,g_1,g_2,v_1,v_2)]} \redxs \config{\prog_1;\prog_2}{E[v]}
$$
If the following preconditions hold where $\iov(\prog_1) = S \cup V$:
\begin{enumerate}
\item $\{ g_1 \} \cap \{ g_2 \} \cap \wired(\prog_1) = \varnothing$ and $g \not\in \prog_1$
\item $\gc{\prog_1}{v_1}{g_1}$ and $\gc{\prog_1}{v_2}{g_2}$
\item $\sep{\progd(\prog_1)}{S_{\{1\}}}{V_{\{2\}}}$
\item $\sep{\progd(\prog_1)}{S_{\{2\}}}{V_{\{1\}}}$
\end{enumerate}
then we have as postconditions where $\iov(\prog_1) = S \cup V'$:
\begin{enumerate}
\item $\gc{\prog_1;\prog_2}{v}{g_2}$
\item $\sep{\progd(\prog_1,\prog_2)}{S_{\{1\}}}{V'_{\{2\}}}$
\item $\sep{\progd(\prog_1,\prog_2)}{S_{\{2\}}}{V'_{\{1\}}}$
\end{enumerate}
\end{lemma}
\begin{proof}
  Given preconditions we have $v_1 =  \{ \ttt{k = }\be^1_{k}; \ttt{p = }\be^1_{p} \}$ and
  $v_2 = \{ \ttt{k = }\be^2_{k}; \ttt{p = }\be^2_{p} \}$ for some
  $\be^1_{k}$,$\be^2_{k}$,$\be^1_{p}$,$\be^2_{p}$ with correlations as per Definition
  \ref{definition-gc}.
  %\begin{eqnarray*}
  %  v_1 &=& \{ \ttt{k = }\be^1_{k}; \ttt{p = }\be^1_{p} \} \\
  %  v_2 &=& \{ \ttt{k = }\be^2_{k}; \ttt{p = }\be^2_{p} \}
  %\end{eqnarray*}
  Let $\prog$ be as defined in Definition \ref{definition-ygcgate-certification}.
  We observe:
  \begin{eqnarray*}
    &\prog_2 = \\
    &{\small \prog[\be^1_{k}/\ttt{flip[2,gate:a.k]}][\be^1_{p}/\ttt{flip[2,gate:a.p]}][\be^2_{k}/\ttt{flip[2,gate:b.k]}][\be^1_{p}/\ttt{flip[2,gate:b.p]}]}
  \end{eqnarray*}
  Given that $g_1$ and $g_2$ are distinct and not wired in $\prog_1$
  we are assured that $\ttt{owl}(g_1)$ and $\ttt{owl}(g_1)$ are in
  independent uniform distributions, and given that $g \not\in
  \prog_1$ we are assured that $\ttt{owl}(g)$ contains entirely fresh
  flips. Thus by condition (i) of Definition \ref{definition-ygcgate-certification} and
  Lemma \ref{lemma-substitution} we have:
  $$
  \sep{\prog_1;\prog_2}{\vars(\be^1_{k},\be^2_{k},\be^1_{p},\be^2_{p})}{\vdefs(\prog_2)}
  $$
  Thus by Lemmas \ref{lemma-noninterference} and \ref{lemma-separation} we establish
  postconditions (ii) and (iii).

  Also since $v_1$ and $v_2$ are correlated either positively or negatively with
  $\ttt{owl}(g_1)$ and $\ttt{owl}(g_2)$ respectively by precondition (ii),
  by Definition \ref{definition-gc}, precondition (i), and Lemma \ref{lemma-substitution-sim}
  we establish postcondition (i), since Definition \ref{definition-ygcgate-certification}
  requires gate output correlation with $\ttt{owl}(g)$ given any input valence conditions.
\end{proof}

\begin{lemma}[YGC Encode Invariant]
  \label{lemma-ygc-encode}
Given well-typed $\prog_1;E[\mathit{encode}(s_1,s_2)]$ and certified $\mathit{encode}$ where 
$$
\config{\prog_1}{E[\ttt{encode}(s_1,s_2)]} \redxs \config{\prog_1;\prog_2}{E[\ttt{\{wv1=}v_1\ttt{;wv2=}v_2\ttt{\}}]}
$$
If the following preconditions hold where $\iov(\prog_1) = S \cup V$:
\begin{enumerate}
\item $\sep{\progd(\prog_1)}{S_{\{1\}}}{V_{\{2\}}}$
\item $\sep{\progd(\prog_1)}{S_{\{2\}}}{V_{\{1\}}}$
\end{enumerate}
then we have as postconditions where $\iov(\prog_1) = S' \cup V'$:
\begin{enumerate}
\item $\gc{\prog_1;\prog_2}{v_1}{s_1}$ and $\gc{\prog_1}{v_2}{s_2}$
\item $\sep{\progd(\prog_1;\prog_2)}{S'_{\{1\}}}{V'_{\{2\}}}$
\item $\sep{\progd(\prog_1;\prog_2)}{S'_{\{2\}}}{V'_{\{1\}}}$
\end{enumerate}
\end{lemma}
\begin{proof}
  By Definition \ref{definition-ygcencode-certification} we have:
  \begin{mathpar}
    \sep{\progtt(\prog_2)}{\ttt{\{s[1,s1]\}}}{\vdefs(\prog_2)_{\{2\}}}

    \sep{\progtt(\prog_2)}{\ttt{\{s[2,s2]\}}}{\vdefs(\prog_2)_{\{1\}}}
  \end{mathpar}
  Since we assume that secrets are in uniform and independent marginal
  distributions a priori, and $\vars(\prog_1) \cap \vars(\prog_2) =
  \varnothing$ by condition (iv) of Definition
  \ref{definition-ygcencode-certification} and assumptions of
  well-typedness, conditions (ii-iii) follow by Lemmas
  \ref{lemma-noninterference} and \ref{lemma-separation}. Also by
  Definition \ref{definition-ygcencode-certification} we have
  $\gc{\prog_2}{v_1}{s_1}$ and $\gc{\prog_2}{v_1}{s_1}$, so also
  $\gc{\prog_1;\prog_2}{v_1}{s_1}$ and
  $\gc{\prog_1;\prog_2}{v_1}{s_1}$ by condition (iv) of Definition
  \ref{definition-ygcencode-certification} and Lemmas
  \ref{lemma-noninterference} and \ref{lemma-separation}.
\end{proof}

Given the above, we can now establish that any circuit built with
certified components is passive secure.  Note that we assume a normal
form of programs where the last instruction is a decoding and public
reveal of the output, and we require that no gate is wired more than once.
\cnote{There is another subtlety here, that gates are wired correctly
  in the sense that if the garbler generates a table with input wire label
  $g_1$ then only $g_1$ is wired to that input. I'll modify the
  typing to enforce this.}
\begin{theorem}
  \label{theorem-ygc-NIMO}
  If $\eassign{\outv}{\ttt{decode}(g,e)}$ is a well-typed YGC circuit
  definition using certified components where no gate output is wired
  more than once, and
  $\config{\varnothing}{\eassign{\outv}{\ttt{decode}(g,e)}} \redxs
  \config{\prog}{\varnothing}$, then $\NIMO(\prog)$.
\end{theorem}

\begin{proof}
  By assumptions of well-typedness we
  have for some $\be_k$, $\be_p$, and $\be$:
  $$
  \config{\varnothing}{\eassign{\outv}{\ttt{decode}(g,e)}} \redxs
  \config{\prog_1}{\eassign{\outv}{\ttt{decode}(g,\{ \ttt{k = }\be_k;  \ttt{p = }\be_p\})}}
  \redxs \config{\prog_1;\prog_2}{\eassign{\outv}{\be}}
  $$
  Let $\iov(\prog_1) = S \cup V$.
  By Lemmas \ref{lemma-ygc-encode} and \ref{lemma-ygc-preservation} we
  have $\sep{\progd(\prog_1)}{S_{\{1\}}}{V_{\{2\}}}$ and
  $\sep{\progd(\prog_1)}{S_{\{2\}}}{V_{\{1\}}}$.
  Let $\prog$ be as defined in Definition \ref{definition-ygdecode-certification}.
  We observe:
  \begin{eqnarray*}
    & \prog_2 = \\ 
    & \prog[\be_k/\ttt{\{flip[2,gate:c.k]}][\be_p/\ttt{flip[2,gate:c.p]}]
  \end{eqnarray*}
  so also by  Definition \ref{definition-ygdecode-certification} and
  Lemma \ref{lemma-substitution} we have:
  $$
  \sep{\progtt(\prog_1;\prog_2)}{\vars(\be_k,\be_p)}{\vdefs(\prog_2)}
  $$
  so, letting $\iov(\prog_1;\prog_2) = S \cup V'$ by
  Lemmas \ref{lemma-noninterference} \ref{lemma-separation} we have
  $\sep{\progd(\prog_1;\prog_2)}{S_{\{1\}}}{V'_{\{2\}}}$ and
  $\sep{\progd(\prog_1;\prog_2)}{S_{\{2\}}}{V'_{\{1\}}}$.
  Thus, letting $\prog' \defeq (\prog_1;\prog_2;\eassign{\outv}{\be})$, for all $\beta$:
  $$\sep{\condd{\progd(\prog')}{S_{\{1\}} \cup V_{\{2\}}}{\{ \outv \mapsto \beta \}}}{S_{\{1\}}}{V_{\{2\}}}
  \quad \text{and} \quad
    \sep{\condd{\progd(\prog')}{S_{\{2\}} \cup V_{\{1\}}}{\{ \outv \mapsto \beta \}}}{S_{\{2\}}}{V_{\{1\}}}$$
  thus for all $\store \in \mems(V_2 \cup \{ \outv \})$:
  $$\condd{\progd(\prog')}{S_{\{1\}}}{\store}
  = \condd{\progd(\prog')}{S_{\{1\}}}{\store_{\{\outv\}}}$$
  and for all $\store \in \mems(V_1 \cup \{ \outv \})$:
  $$\condd{\progd(\prog')}{S_{\{2\}}}{\store}
  = \condd{\progd(\prog')}{S_{\{2\}}}{\store_{\{\outv\}}}$$
  establishing the result by Lemma \ref{lemma-nimo} and Definition \ref{definition-NIMO}.
\end{proof}

@@

Theorems \ref{theorem-gmw-NIMO} \ref{theorem-ygc-NIMO} means that any
well-typed program using certified components will generate a circuit
that is passive secure. To add an $\ttt{or}$ gate to our YGC library,
for example, we can use $\ttt{andgg}$ as a template, in fact simple
modification of $\ttt{andtable}$ is all that would be needed. Thus,
this library embodies a Fairplay-like language where well-typedness of
metaprograms guarantees safety and security of generated protocols.

The requirements that output wire labels are not used more than once
in YGC reflects a known result, that naive copy gate output is unsound
in YGC- i.e., passive security fails. In fact, we are unable to
automatically verify $\gNIMO$ for $\ttt{andgg}$ without the assumption
that input wire lables are in independent uniform distributions. We
can capture the necessary fix as in Figure \ref{fig-ygc-copy}. The
garbler creates a copy gate with two new output wire labels in
independent uniform distributions (in \ttt{copygate}), and permutes
them using the input wire label pointer after encrypting with the
input wire label keys. The evaluator then recovers the encrypted
output wire values during evaluation (in \ttt{evalcopy}). Given an
$\ttt{orgg}$ gate defined as outlined abotve, we can then use secure
$\ttt{copy}$ as follows:
\begin{verbatimtab}
  let s = encode(s1,s2) in
  let s1c = copy(c1s1,c2s1,s1,s.wv1) in
  let s2c = copy(c1s2,c2s2,s2,s.wv2) in
  let wv1 = andgg(1,c1s1,c1s2,s1c.wv1,s2c.wv1) in
  let wv2 = orgg(2,c2s1,c2s2,s1c.wv2,s2c.wv2) in
  decode(3,andgg(3,1,2,wv1,wv2))
\end{verbatimtab}
These definitions of $\ttt{copy}$ and $\ttt{orgg}$ have been
automatically verified as in Section \ref{section-pre-post} for
$\ttt{andgg}$. In general, any new gate form- such as optimized gates
\cite{XXX}- can be verified automatically in a similar way.
